Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2018-01-11 2018-IPMU/Gamification/paper.tex
results
Finished spell-check and revision
All that's left is @fergunet revision (and adding himself as an author)

This trade-off between ease of use, allowing users to
participate by just visiting a web page, and personalization, making
registration a requirement in order to % I just simplified the sentence -Mario
participate, is what we will analyze in this paper. In a socio-technical system such as this one, every
decision the user has to take has an influence on the overall
performance, and registration could be seen as a hurdle to volunteers
trying to participate in an ephemeral experiment, so it is a challenge
to analyze what actually happens in this case; quite clearly, the
inclusion of gamification techniques has an impact on page loading and
complexity of server-side programming; if the number of users
or the amount of time they contribute to the experiment is not enough,
it would be better to revert NodIO to a purely anonymous system.

@@

% \begin{table}[h!tbp]
%   \small
%   \caption{ Log file record structure}
%   \label{tab:record}
%   \centering
%   \small
%   \begin{tabular}{l  l}
%     \hline\noalign{\smallskip}
%     Attribute & Value \\
%     \noalign{\smallskip}\hline\noalign{\smallskip}
%     chromosome   & The individual sent to the server as a string of 160 bits.  \\ \hline
%     fitness & fitness as an integer.  \\ \hline
%     IP & IP address of the participant (later anonymized) .\\ \hline
%     user & user-name or the string `anonymous'.  \\ \hline
%     worker\_uuid & unique identifier of the HTTP Worker that sent the participation.   \\ \hline
%     level &  level of user or the string `info' \\ \hline
%     message & Only PUT messages were recorded in this experiment. \\ \hline
%     timestamp & A time-stamp based on the Unix epoch\\ \hline
%   \end{tabular}
% \end{table}
%
At the end of the experiment the resulting log file
%(whose fields are shown in Table \ref{tab:record})
contained 933,513 contributions both
registered users and anonymous volunteers. Registered users were responsible for about
90\% of the contributions, while being only 16\% of the total number of unique users (assuming each IP is from a single user).
% The data recorded in JSON format for every contribution is  presented
% in Table~\ref{tab:record}.

>>>>

This trade-off between ease of use, allowing users to
participate by just visiting a web page, and customization, making
registration a requirement in order to % I just simplified the sentence -Mario
participate, is what we will analyze in this paper. In a socio-technical system such as this one, every
decision the user has to take has an influence on the overall
performance, and registration could be seen as a hurdle to volunteers
trying to participate in an ephemeral experiment, so it is a challenge
to analyze what actually happens in this case; quite clearly, the
inclusion of gamification techniques has an impact on page loading and
complexity of server-side programming; if the number of users
or the amount of time they contribute to the experiment is not enough,
it would be better to revert NodIO to a purely anonymous system.

@@

% \begin{table}[h!tbp]
%   \small
%   \caption{ Log file record structure}
%   \label{tab:record}
%   \centering
%   \small
%   \begin{tabular}{l  l}
%     \hline\noalign{\smallskip}
%     Attribute & Value \\
%     \noalign{\smallskip}\hline\noalign{\smallskip}
%     chromosome   & The individual sent to the server as a string of 160 bits.  \\ \hline
%     fitness & fitness as an integer.  \\ \hline
%     IP & IP address of the participant (later anonymized) .\\ \hline
%     user & user-name or the string `anonymous'.  \\ \hline
%     worker\_uuid & unique identifier of the HTTP Worker that sent the participation.   \\ \hline
%     level &  level of user or the string `info' \\ \hline
%     message & Only PUT messages were recorded in this experiment. \\ \hline
%     timestamp & A time-stamp based on the Unix epoch\\ \hline
%   \end{tabular}
% \end{table}
%
At the end of the experiment the resulting log file
%(whose fields are shown in Table \ref{tab:record})
contained 933,513 contributions considering both
registered and anonymous volunteers. Registered users were responsible for about
90\% of the contributions, while being only 16\% of the total number of unique users (assuming each IP is from a single user).
% The data recorded in JSON format for every contribution is  presented
% in Table~\ref{tab:record}.
